## vegalite {.tabset}
```{r, include=FALSE}
knitr::read_chunk("vegalite.R")
```

[Vega](http://vega.github.io/vega/) is a grammar of graphics implementation that takes JSON and converts the results to HTML5 or SVG. [Vega-Lite](https://vega.github.io/vega-lite/) provides layer over the top of Vega to reduce the burden of generating the JSON specifications required.

[Bob Rudis](http://rud.is/) developed an R binding of vegalite, currently available on github( [hrbrmstr/vegalite](https://github.com/hrbrmstr/vegalite) ). 

Much of the code used in this is taken from, or loosely based on, the code Bob wrote in [his reproduction](http://rud.is/projects/vegalite01.html) of the Vega gallery.

Limitations:

 - Can't produce boxplots
 - vegalite does not produce interactive charts

```{r setup, results='hide', warning=FALSE, message=FALSE, echo=TRUE}
```

### Basic

#### Bar chart
```{r barchart}
```

```{r aggbarchart}
```

```{r groupedbarchart}
```

#### Scatter plot
```{r scatterplot}
```

```{r scatterplotcircles}
```

```{r binnedscatterplot}
```

```{r colouredscatterplot}
```

```{r colouredtextscatterplot}
```

```{r scatterplotlogscale}
```

```{r bubblechart}
```

#### Line chart

```{r linechart}
```

```{r multiserieslinechart}
```

#### Others
```{r histogram}
```

```{r areachart}
```

```{r boxplot}
```

### Stacked and Layered Plots 
```{r stackedbar}
```

```{r horizstackedbar}
```

```{r normalisedstackedbar}
```

```{r stackedarea}
```

```{r normalisedstackedarea}
```

```{r layeredbar}
```

### Trellis Plots 
```{r trellisbar}
```

```{r trellisstackedbar}
```

```{r trellisscatter}
```

```{r trellishistogram}
```

```{r trelliscolouredscatterplot}
```

### Uncommon charts
```{r steamgraph}
```

```{r networkgraph}
```

```{r beechart}
```

```{r stripplot}
```

```{r slopegraph}
```
